---
title: >
  The `annoFuseData` User's Guide
author:
- name: Federico Marini
  affiliation: 
  - &id1 Institute of Medical Biostatistics, Epidemiology and Informatics (IMBEI), Mainz
  - Center for Thrombosis and Hemostasis (CTH), Mainz
  email: marinif@uni-mainz.de
- name: Krutika Gaonkar
  affiliation: 
  - &id2 Center for Data-Driven Discovery in Biomedicine, Children’s Hospital of Philadelphia, USA
  email: gaonkark@chop.email.edu
date: "`r BiocStyle::doc_date()`"
package: "`r BiocStyle::pkg_ver('annoFuseData')`"
output: 
  BiocStyle::html_document:
    toc_float: true
    number_sections: true
vignette: >
  %\VignetteIndexEntry{The annoFuseData User's Guide}
  %\VignetteEncoding{UTF-8}  
  %\VignettePackage{annoFuseData}
  %\VignetteKeywords{Software, Transcription, Visualization, GeneExpression, Annotation,
    GeneFusionDetection, GUI, ReportWriting}
  %\VignetteEngine{knitr::rmarkdown}
---  

<style type="text/css">
.smaller {
  font-size: 10px
}
</style>

**Compiled date**: `r Sys.Date()`

**Last edited**: 2020-11-11

**License**: `r packageDescription("annoFuseData")[["License"]]`

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment  = "#>",
  error    = FALSE,
  warning  = FALSE,
  eval     = TRUE,
  message  = FALSE,
  fig.width = 10
)
options(width = 100)
```

---

# Datasets for `annoFuse`

```{r}
library("annoFuseData")
```

### Example output files from fusion callers {-}

* `arriba_example.tsv`
* `starfusion_example.tsv`

```{r}
ff_arriba <- read.delim(system.file("extdata", "arriba_example.tsv", package = "annoFuseData"))
ff_starfusion <- read.delim(system.file("extdata", "starfusion_example.tsv", package = "annoFuseData"))
head(ff_arriba)
head(ff_starfusion)
```

These files are e.g. used in the `annoFuse_single_sample()` function.

### Expression data {-}

* `example.rsem.genes.results.gz`

```{r}
expression_tbl <- read.delim(system.file("extdata", "example.rsem.genes.results.gz", package = "annoFuseData"))
head(expression_tbl)
```


### Examples of output files from the `annoFuse` workflow {-}

* `FilteredFusionAnnoFuse.tsv`
* `PutativeDriverAnnoFuse.tsv`

```{r}
out_annofuse_putative <- read.delim(
  system.file("extdata", "PutativeDriverAnnoFuse.tsv", package = "annoFuseData"))
out_annofuse_filtered <- read.delim(
  system.file("extdata", "FilteredFusionAnnoFuse.tsv", package = "annoFuseData"))

head(out_annofuse_putative)
head(out_annofuse_filtered)
```

### Adding domain level information and exon information {-}

Will describe and give some initial overview on each dataset:

* `pfamDataBioMart.RDS`
* `exonsToPlot.RDS`

```{r}
data_pfam <- readRDS(system.file("extdata", "pfamDataBioMart.RDS", package = "annoFuseData"))
head(data_pfam)
data_exons <- readRDS(system.file("extdata", "exonsToPlot.RDS", package = "annoFuseData"))
head(data_exons)
dim(data_exons)
```

### Analysis of TCGA data {-}

* `merged_arriba_tcga.tsv`
* `merged_starfusion_tcga.tsv`
* `sample_aliquot_tcga.tsv`
* `final_fusion_mmc2.txt`

```{r}
tcga_arriba_df <- read.delim(system.file("extdata", "merged_arriba_tcga.tsv", package = "annoFuseData"))
tcga_starfusion_df <- read.delim(system.file("extdata", "merged_starfusion_tcga.tsv", package = "annoFuseData"))

head(tcga_arriba_df)
head(tcga_starfusion_df)

tcga_manifest <- read.delim(system.file("extdata", "sample_aliquot_tcga.tsv", package = "annoFuseData"))
final_fusion <- read.delim(system.file("extdata", "final_fusion_mmc2.txt", package = "annoFuseData"))

head(tcga_manifest)
head(final_fusion)
```


### Scoring the annotated fusion calls {-}

zscored_annotation

* `expr_collapsed.rds`
* `gtex_collapsed.rds`

```{r}
expressionMatrix <- readRDS(system.file("extdata", "expr_collapsed.rds", package = "annoFuseData"))
normData <- readRDS(system.file("extdata", "gtex_collapsed.rds", package = "annoFuseData"))

head(expressionMatrix)
head(normData)
```



### Reference tables for gene lists and fusions {-}

fusion_driver

* `genelistreference.txt`
* `fusionreference.txt`


```{r}
geneListReferenceDataTab <- read.delim(
  system.file("extdata", "genelistreference.txt", package = "annoFuseData"), 
  stringsAsFactors = FALSE)
fusionReferenceDataTab <- read.delim(
  system.file("extdata", "fusionreference.txt", package = "annoFuseData"), 
  stringsAsFactors = FALSE)
head(geneListReferenceDataTab)
head(fusionReferenceDataTab)
```


# Session info {- .smaller}

```{r}
sessionInfo()
```


